Autonomous Exploration with Exact Inverse Sensor Models

### 2018-06-09 Journal/JINT 2017/JIRS16_rev1.tex
journal added

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{amsmath,amssymb,url,times}%,subfigure}% amsthm is the one!
\usepackage{caption,subcaption,hyperref}
\usepackage{color,comment}
\usepackage{curves,pgfgantt}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
 \journalname{Journal of Intelligent \& Robotic Systems}

\newtheorem{prop}{Proposition}
\newcommand{\norm}[1]{\ensuremath{\left\| #1 \right\|}}
\newcommand{\abs}[1]{\ensuremath{\left| #1 \right|}}
\newcommand{\bracket}[1]{\ensuremath{\left[ #1 \right]}}
\newcommand{\braces}[1]{\ensuremath{\left\{ #1 \right\}}}
\newcommand{\parenth}[1]{\ensuremath{\left( #1 \right)}}
\newcommand{\ip}[1]{\ensuremath{\langle #1 \rangle}}
\newcommand{\refeqn}[1]{(\ref{eqn:#1})}
\newcommand{\reffig}[1]{Figure \ref{fig:#1}}
\newcommand{\tr}[1]{\mbox{tr}\ensuremath{\negthickspace\bracket{#1}}}
\newcommand{\trs}[1]{\mbox{tr}\ensuremath{\!\bracket{#1}}}
\newcommand{\deriv}[2]{\ensuremath{\frac{\partial #1}{\partial #2}}}
\newcommand{\G}{\ensuremath{\mathsf{G}}}
\newcommand{\SO}{\ensuremath{\mathsf{SO(3)}}}
\newcommand{\T}{\ensuremath{\mathsf{T}}}
\renewcommand{\L}{\ensuremath{\mathsf{L}}}
\newcommand{\so}{\ensuremath{\mathfrak{so}(3)}}
\newcommand{\SE}{\ensuremath{\mathsf{SE(3)}}}
\newcommand{\se}{\ensuremath{\mathfrak{se}(3)}}
\renewcommand{\Re}{\ensuremath{\mathbb{R}}}
\newcommand{\Sph}{\ensuremath{\mathsf{S}}}
\newcommand{\aSE}[2]{\ensuremath{\begin{bmatrix}#1&#2\\0&1\end{bmatrix}}}
\newcommand{\ase}[2]{\ensuremath{\begin{bmatrix}#1&#2\\0&0\end{bmatrix}}}
\newcommand{\D}{\ensuremath{\mathbf{D}}}
\renewcommand{\d}{\ensuremath{\mathbf{d}}}
\newcommand{\pair}[1]{\ensuremath{\left\langle #1 \right\rangle}}
\newcommand{\met}[1]{\ensuremath{\langle\!\langle #1 \rangle\!\rangle}}
\newcommand{\Ad}{\ensuremath{\mathrm{Ad}}}
\newcommand{\ad}{\ensuremath{\mathrm{ad}}}
\newcommand{\g}{\ensuremath{\mathfrak{g}}}
\newcommand{\argmin}{\operatornamewithlimits{argmin}}
\newcommand{\argmax}{\operatornamewithlimits{argmax}}
\graphicspath{{./Fig/}}

@@

In this paper, we propose an autonomous exploration technique based on expected entropy change that avoids the aforementioned issues. 
%The occupancy grid mapping scheme is based on~\cite{KauLeeAiMos16}, which provides the exact solution of occupancy grid mapping of a single measurement ray. 
We develop a solution for expected entropy gain based on exact occupancy grid mapping~\cite{KauLeeAiMos16}. This solution directly calculates expected entropy from a probabilistic map based on similar assumptions of those applied to occupancy grid mapping.
Though more accurate than several other approaches, the proposed solution requires large computational resources, making real-time implementation difficult in certain scenarios.
Thus, we provide the tools to approximate the exact solution that reduces the computational requirements with realistic assumptions.
The motion of the robot is formulated as an optimization problem, where the expected entropy change is minimized, or equivalently the expected information gain is maximized.
Compared with the recent results (e.g. [12], [13], [16], [17]) that employ Rao-Blackwellized particle filters to deal with localization and autonomous exploration simultaneously with an approximate entropy change, this paper is based on an accurate probabilistic solution to map information gain, under the assumption that the robot pose is known.

@@

\subsection{Probabilistic Occupancy Grid Mapping}
\label{subsec:POGM}
Let a map $m$ be decomposed into $n_m$ evenly-spaced grid cells, where the $i$-th grid cell is assigned to a static binary random variable $\mathbf{m}_i$ for $i\in\braces{1,2,\ldots,n_m}$, that is defined as $\mathbf{m}_i=1$ when occupied, and $\mathbf{m}_i=0$ when free. The location and size of each grid cell is assumed known. Therefore, a map $m$ is defined by $\{\mathbf{m}_1,\ldots, \mathbf{m}_{n_m}\}$ ($2^{n_{m}}$ possible maps).

@@

Suppose at time $t$, $P(m|X_{1:t},Z_{1:t})$ is given. Let $X_c$ be a candidate pose under consideration for some future time step.
The expected information gain $\mathcal I(X_c)$ is defined as the negative change of entropy
\begin{align}
\label{eqn:ObjFun}
\mathcal I(X_c)&=H(P(m|X_{1:t},Z_{1:t}))%\nonumber\\&\quad
-\text{E}\left[H(P(m|X_{1:t},Z_{1:t},X_c,Z_c))\right],
\end{align}
where $H(P(m|X_{1:t},Z_{1:t}))$ may be computed with \refeqn{ShannonsEntropyDef} and \\$\text{E}\left[H(P(m|X_{1:t},Z_{1:t},X_c,Z_c))\right]$ is the expected entropy when the robot is located at $X_c$, where the expectation is taken over $Z_c$.
Since autonomous exploration is formulated as a trajectory optimization, the goal is to repeatedly choose optimal $X_c^*$ that maximizes the objective function
\begin{align}
\label{eqn:Objective}
X_c^*=\argmax_{X_c}{\mathcal I(X_c)},
\end{align}
where $X_c^*$ satisfies the inequality constraint to avoid collisions,
\begin{align}
\label{eqn:CollisionInequalityConstraint}
P_\text{collision}(X)=1-\prod_{i\in\mathcal C_X}P(\bar{\mathbf{m}}_i|X_{1:t},Z_{1:t})\leq\beta,
\end{align}
where $\mathcal C_X$ is the set of grid cells falling inside a volume of preselected size around $X$ that may cause collision and $\beta>0$ is a threshold of the probability of collision.
Once the robot has translated to $X_c^*$, the above process is repeated.

@@

\paragraph{Bayesian Framework}
%Assuming that the probability density of thxe sensor measurement is fixed over a small measurement region $\Delta z$, 
Bayes' rule yields
%First, Bayes' rule is applied for a particular map $m$ and arbitrarily small measurement region $\Delta z$, yielding
\begin{align}
\label{eqn:BayesRuleRayISM}
P(&m|z_{t,l},X_{1:t},Z_{1:t-1})%\nonumber\\&
=\frac{p(z_{t,l}|m,X_{1:t},Z_{1:t-1})P(m|X_{1:t-1},Z_{1:t-1})}{p(z_{t,l}|X_{1:t},Z_{1:t-1})},
\end{align}
considering that $X_t$ carries no information about $m$ without $Z_t$.
If the current pose $X_t$ and map $m$ are known, then the measurement ray $z_{t,l}$ is independent of past poses $X_{1:t-1}$ and past measurements $Z_{1:t-1}$ to obtain
%Note that this is contrary to approaches that consider $X_t$ and $\mathbf{m}_i$ (not the full map $m$) as enough information, ignoring the occupancy of other cells in this term.
%Then, \refeqn{BayesRuleRayISM} can be rewritten as
\begin{align}
P(m|z_{t,l},&X_{1:t},Z_{1:t-1})%\nonumber\\&
=\eta_{t,l}p(z_{t,l}|m,X_{t})P(m|X_{1:t-1},Z_{1:t-1}),
\end{align}
where the normalizing constant $\eta_{t,l}\in\Re$ absorbs all terms that do not depend on the map $m$.

@@

We propose a computational algorithm to evaluate \refeqn{InvSenModWithProbDens} efficiently. 
Since the cells outside of the sensor field of view (FOV) are not affected, we focus on a reduced map $r_l$ in the FOV of the $l$-th ray. This reduced map is chosen such that each cell of $r_l$ corresponds to a grid cell of $m$ that the $l$-th ray intersects, ordered by increasing distance, which is easily determined from geometry. Let $\mathbf{r}_{l,k}$ be the binary random variable representing the occupancy of the $k$-th cell of the $l$-th ray. The number of cells in the reduced map is denoted by $n_{r,l}\leq n_m$.

Next, let $\mathbf{r}_{l,k+}$ correspond to the event that the $k$-th cell of the $l$-th ray is occupied, cells with lower index are free, and cells with greater index may or may not be occupied, i.e., event $\mathbf{r}_{l,k+}$ occurs when \\$r\in\braces{r\in\{0,1\}^{{n_{r,l}}}\,|\mathbf{r}_{l,1}=0,\mathbf{r}_{l,2}=0,\ldots,\mathbf{r}_{l,k-1}=0,\mathbf{r}_{l,k}=1}$. In other words, the $k$-th cell $\mathbf{r}_{l,k}$ is the closest occupied cell to current pose $X_t$ along the $l$-th ray, and this concept is illustrated with a simple 1D example in Figure \ref{fig:show_rkplus}.
\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{rkplus_1.png}
    \centering
  \includegraphics[width=0.4\textwidth]{rkplus_2.png}  
  \centering
  \includegraphics[width=0.4\textwidth]{rkplus_3.png}
    \centering
  \includegraphics[width=0.4\textwidth]{rkplus_4.png}
  \caption{A robot located to the left of the 1D occupancy grid map $r_l$ composed of $n_{r,l}=6$ grid cells in $4$ cases. In each case, cells $1$--$3$ are free, cell $4$ is occupied, and cells $5$ and $6$ may or may not be occupied. Each case corresponds to the event $\mathbf{r}_{4+}$.}
  \label{fig:show_rkplus}
\end{figure}
Then, the forward sensor model is identical for all maps defined by $\mathbf{r}_{l,k+}$, regardless of the occupancy of the cells beyond the $k$-th cell, and the corresponding forward sensor model $p(z_{t,l}|\mathbf{r}_{l,k+},X_{t})$ depends on the distance from $X_t$ to the $k$-th cell. Based on this, we present the following computational algorithm to compute the inverse sensor model.

\begin{prop}
For the $l$-th measurement ray, the a posteriori probability of the occupancy of the $k$-th cell, namely the ray inverse sensor model, is given by
\begin{align}
\label{eqn:RayISMAnswer}
P(\mathbf{r}_{l,k}|z_{t,l},X_{1:t},Z_{1:t-1})&=\eta_{t,l}\tilde P(\mathbf{r}_{l,k}|z_{t,l},X_{1:t},Z_{1:t-1}),
\end{align}
where the unnormalized probability of the inverse sensor model is defined as
\begin{align}
\label{eqn:Unnormalized}
& \tilde P(\mathbf{r}_{l,k}|z_{t,l},X_{1:t},Z_{1:t-1})%\nonumber\\&
=P(\mathbf{r}_{l,k}|X_{1:t-1},Z_{1:t-1})\nonumber\\
&\quad\times 
\bigg[\sum_{i=1}^{k-1}\bigg\{\prod_{j=0}^{i-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1})\bigg\}%\nonumber\\
%&\quad\times 
p(z_{t,l}|\mathbf{r}_{l,i+},X_t)P(\mathbf{r}_{l,i}|X_{1:t-1},Z_{1:t-1})\bigg]\nonumber\\
&\quad + \bigg\{\prod_{j=0}^{k-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1})\bigg\}%\nonumber\\
%&\quad\times 
p(z_{t,l}|\mathbf{r}_{l,k+},X_t)P(\mathbf{r}_{l,k}|X_{1:t-1},Z_{1:t-1}),
\end{align}
where $P(\bar{\mathbf{r}}_{l,0}|X_{1:t-1},Z_{1:t-1})=P(\mathbf{r}_{l,n_r+1}|X_{1:t-1},Z_{1:t-1})=1$ is chosen for convenience and $p(z_{t,l}|\mathbf{r}_{l,(n_r+1)+},X_t)$ represents the forward sensor model of a maximum sensor reading. The normalizer $\eta_{t,l}$ is given by
\begin{align}
\label{eqn:allEta}
\eta_{t,l}
&=
\bigg[\sum_{i=1}^{n_{r,l}+1}\bigg\{\prod_{j=0}^{i-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1})\bigg\}\nonumber\\&\quad\times p(z_{t,l}|\mathbf{r}_{l,i+},X_t)P(\mathbf{r}_{l,i}|X_{1:t-1},Z_{1:t-1})\bigg]^{-1},
\end{align}
and it is independent of the cell index $k$.
\end{prop}
\begin{proof}
See Appendix.
\end{proof}

@@

\subsection{Summary of Algorithm}

In short, the proposed scan inverse sensor model is computed by \refeqn{RayISMAnswer}-\refeqn{RayByRayScanISM}. These are summarized in Table \ref{tab:RayByRayISM} as a computationally efficient, recursive algorithm that avoids several repeated calculations of the same quantity. This algorithm utilizes temporary variables, where the required computational resources are minimized by computing the updated occupancy probabilities of all grid cells along a measurement ray together.

@@

% More simple (subscripts omitted)
\begin{table}[p]
\begin{tabular}{ l }
  Function: $P(\mathbf{r}_k|z)=\text{InverseSensorModel}(P(\mathbf{r}_k),z)$\\
  for all $k\in\braces{1,2,\ldots,n_{r}}$\\
  Initialize $\eta^{-1}=0$ and $P(\bar{\mathbf{r}}_{0})=1$;\\
  for all $k = 1,2,\ldots,n_{r}$\\
   \ \ $P(\mathbf{r}_{k+}) = P(\bar{\mathbf{r}}_{0:k-1})P(\mathbf{r}_{k})$;\\
   \ \ $P(\bar{\mathbf{r}}_{0:k})=P(\bar{\mathbf{r}}_{0:k-1})P(\bar{\mathbf{r}}_{k})$;\\
   \ \ $a_\text{temp}=P(\mathbf{r}_{k+})p(z_l|\mathbf{r}_{k+},X)$;\\
   \ \ $\tilde P(\mathbf{r}_{k}|z)=P(\mathbf{r}_{k})\eta^{-1}_{t,l}+a_\text{temp}$;\\
   \ \ $\eta^{-1}=\eta^{-1}+a_\text{temp}$;\\
  end for\\
  $\eta^{-1}=\eta^{-1}+P(\bar{\mathbf{r}}_{0:k})p(z_\text{max})$;\\
  $P(\mathbf{r}_{k}|z)=\eta\tilde P(\mathbf{r}_{k}|z)$ for all $k\in\braces{1,2,\ldots,n_{r}}$;\\
  \end{tabular}
\caption{Inverse Sensor Model of an Individual Measurement Ray}
\raggedright{Note: this function is only considering $l$-th ray at the $t$-th time step, where probabilities are subject to conditions on $X_{1:t},Z_{1:t-1},z_{t,1:l-1}$, so these are removed from the algorithm for simplicity.}
\label{tab:RayByRayISM}
\end{table}

@@

We present an algorithm pseudocode providing the necessary steps to obtain the objective function for a single measurement ray (Table \ref{tab:RayExpectedEntropyGain}). Much like the algorithm pseudocode for the inverse sensor model (Table \ref{tab:RayByRayISM}), the variable $a_\text{temp}$ serves as an intermediate variable designed to avoid repeated calculations.
Since this algorithm operates as a function, fixed indices and condition variables are removed for simplification.

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{amsmath,amssymb,url,times}%,subfigure}% amsthm is the one!
\usepackage{caption,subcaption,hyperref}
\usepackage{color,comment}
\usepackage{curves,pgfgantt}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}

% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
 \journalname{Journal of Intelligent \& Robotic Systems}

\newtheorem{prop}{Proposition}
\newcommand{\norm}[1]{\ensuremath{\left\| #1 \right\|}}
\newcommand{\abs}[1]{\ensuremath{\left| #1 \right|}}
\newcommand{\bracket}[1]{\ensuremath{\left[ #1 \right]}}
\newcommand{\braces}[1]{\ensuremath{\left\{ #1 \right\}}}
\newcommand{\parenth}[1]{\ensuremath{\left( #1 \right)}}
\newcommand{\ip}[1]{\ensuremath{\langle #1 \rangle}}
\newcommand{\refeqn}[1]{(\ref{eqn:#1})}
\newcommand{\reffig}[1]{Figure \ref{fig:#1}}
\newcommand{\tr}[1]{\mbox{tr}\ensuremath{\negthickspace\bracket{#1}}}
\newcommand{\trs}[1]{\mbox{tr}\ensuremath{\!\bracket{#1}}}
\newcommand{\deriv}[2]{\ensuremath{\frac{\partial #1}{\partial #2}}}
\newcommand{\G}{\ensuremath{\mathsf{G}}}
\newcommand{\SO}{\ensuremath{\mathsf{SO(3)}}}
\newcommand{\T}{\ensuremath{\mathsf{T}}}
\renewcommand{\L}{\ensuremath{\mathsf{L}}}
\newcommand{\so}{\ensuremath{\mathfrak{so}(3)}}
\newcommand{\SE}{\ensuremath{\mathsf{SE(3)}}}
\newcommand{\se}{\ensuremath{\mathfrak{se}(3)}}
\renewcommand{\Re}{\ensuremath{\mathbb{R}}}
\newcommand{\Sph}{\ensuremath{\mathsf{S}}}
\newcommand{\aSE}[2]{\ensuremath{\begin{bmatrix}#1&#2\\0&1\end{bmatrix}}}
\newcommand{\ase}[2]{\ensuremath{\begin{bmatrix}#1&#2\\0&0\end{bmatrix}}}
\newcommand{\D}{\ensuremath{\mathbf{D}}}
\renewcommand{\d}{\ensuremath{\mathbf{d}}}
\newcommand{\pair}[1]{\ensuremath{\left\langle #1 \right\rangle}}
\newcommand{\met}[1]{\ensuremath{\langle\!\langle #1 \rangle\!\rangle}}
\newcommand{\Ad}{\ensuremath{\mathrm{Ad}}}
\newcommand{\ad}{\ensuremath{\mathrm{ad}}}
\newcommand{\g}{\ensuremath{\mathfrak{g}}}
\newcommand{\argmin}{\operatornamewithlimits{argmin}}
\newcommand{\argmax}{\operatornamewithlimits{argmax}}
\graphicspath{{./Fig/}}
\newcommand{\WriteBlue}[1]{{\color{blue}\protect #1}}

@@

In this paper, we propose an autonomous exploration technique based on expected entropy change that avoids the aforementioned issues. 
%The occupancy grid mapping scheme is based on~\cite{KauLeeAiMos16}, which provides the exact solution of occupancy grid mapping of a single measurement ray. 
We develop a solution for expected entropy gain based on exact occupancy grid mapping~\cite{KauLeeAiMos16}. This solution directly calculates expected entropy from a probabilistic map based on similar assumptions of those applied to occupancy grid mapping.
Though more accurate than several other approaches, the proposed solution requires large computational resources, making real-time implementation difficult in certain scenarios.
Thus, we provide the tools to approximate the exact solution that reduces the computational requirements with realistic assumptions.
The motion of the robot is formulated as an optimization problem, where the expected entropy change is minimized, or equivalently the expected information gain is maximized.
Compared with the recent results (e.g. [12], [13], [16], [17]) that employ Rao-Blackwellized particle filters to deal with localization and autonomous exploration simultaneously with an approximate entropy change, this paper is based on an accurate probabilistic solution to map information gain, under the assumption that the robot pose is known. Accounting for the stochastic properties of position and attitude is important to the field of robotics, and accounting for localization in conjunction with mapping and exploration are considered as a future step to this paper.

@@

\subsection{Probabilistic Occupancy Grid Mapping}
\label{subsec:POGM}
Let a map $m$ be decomposed into $n_m$ evenly-spaced grid cells, where the $i$-th grid cell is assigned to a static binary random variable $\mathbf{m}_i$ for $i\in\braces{1,2,\ldots,n_m}$, that is defined as $\mathbf{m}_i=1$ when occupied, and $\mathbf{m}_i=0$ when free. The location and size of each grid cell is assumed known, where a smaller cell size (greater grid resolution) better represents a space, but increases computation and memory. Therefore, a map $m$ is defined by $\{\mathbf{m}_1,\ldots, \mathbf{m}_{n_m}\}$ ($2^{n_{m}}$ possible maps).

@@

Suppose at time $t$, $P(m|X_{1:t},Z_{1:t})$ is given. Let $X_c$ be a candidate pose under consideration for some future time step.
The expected information gain $\mathcal I(X_c)$ is defined as the negative change of entropy
\begin{align}
\label{eqn:ObjFun}
\mathcal I(X_c)&=H(P(m|X_{1:t},Z_{1:t}))%\nonumber\\&\quad
-\text{E}\left[H(P(m|X_{1:t},Z_{1:t},X_c,Z_c))\right],
\end{align}
where $H(P(m|X_{1:t},Z_{1:t}))$ may be computed with \refeqn{ShannonsEntropyDef} and \\$\text{E}\left[H(P(m|X_{1:t},Z_{1:t},X_c,Z_c))\right]$ is the expected entropy when the robot is located at $X_c$, where the expectation is taken over $Z_c$.
Since autonomous exploration is formulated as a trajectory optimization, the goal is to repeatedly choose optimal $X_c^*$ that maximizes the objective function
\begin{align}
\label{eqn:Objective}
X_c^*=\argmax_{X_c}{\mathcal I(X_c)},
\end{align}
where $X_c^*$ satisfies the inequality constraint to avoid collisions,
\begin{align}
\label{eqn:CollisionInequalityConstraint}
P_\text{collision}(X)=1-\prod_{i\in\mathcal C_X}P(\bar{\mathbf{m}}_i|X_{1:t},Z_{1:t})\leq\beta,
\end{align}
where $\mathcal C_X$ is the set of grid cells falling inside a volume of preselected size around $X$ that may cause collision and $\beta>0$ is a threshold of the probability of collision. It is considered that once a collision-free trajectory toward $X_c^*$ is obtained, the robot moves along the trajectory controlled by a motion control system in the inner loop. Once the robot has translated to $X_c^*$, the above process is repeated.

@@

\paragraph{Bayesian Framework}
%Assuming that the probability density of the sensor measurement is fixed over a small measurement region $\Delta z$, 
The occupancy probability $P(m|z_{t,l},X_{1:t},Z_{1:t-1})$ is based on the forward sensor model $p(z_{t,l}|m,X_{1:t},Z_{1:t-1})$ that describe the distribution of the measurements for the given robot pose and the map. This specifies the stochastic characteristics of the sensor, such as the mean squared error, and it is assumed as a known distribution, specific to a particular depth sensor. One could certainly obtain a stochastic model by fitting a probability density to a controlled set of measurements.
Bayes' rule yields
%First, Bayes' rule is applied for a particular map $m$ and arbitrarily small measurement region $\Delta z$, yielding
\begin{align}
\label{eqn:BayesRuleRayISM}
P(&m|z_{t,l},X_{1:t},Z_{1:t-1})%\nonumber\\&
=\frac{p(z_{t,l}|m,X_{1:t},Z_{1:t-1})P(m|X_{1:t-1},Z_{1:t-1})}{p(z_{t,l}|X_{1:t},Z_{1:t-1})},
\end{align}
considering that $X_t$ carries no information about $m$ without $Z_t$.
If the current pose $X_t$ and map $m$ are known, then the measurement ray $z_{t,l}$ is independent of past poses $X_{1:t-1}$ and past measurements $Z_{1:t-1}$ to obtain
%Note that this is contrary to approaches that consider $X_t$ and $\mathbf{m}_i$ (not the full map $m$) as enough information, ignoring the occupancy of other cells in this term.
%Then, \refeqn{BayesRuleRayISM} can be rewritten as
\begin{align}
P(m|z_{t,l},&X_{1:t},Z_{1:t-1})%\nonumber\\&
=\eta_{t,l}p(z_{t,l}|m,X_{t})P(m|X_{1:t-1},Z_{1:t-1}),
\end{align}
where the normalizing constant $\eta_{t,l}\in\Re$ absorbs all terms that do not depend on the map $m$.

@@

We propose a computational algorithm to evaluate \refeqn{InvSenModWithProbDens} efficiently. 
Since the cells outside of the sensor field of view (FOV) are not affected, we focus on a reduced map $r_l$ in the FOV of the $l$-th ray. This reduced map is chosen such that each cell of $r_l$ corresponds to a grid cell of map $m$ that the $l$-th ray intersects, ordered by increasing distance, which is easily determined from geometry. Let $\mathbf{r}_{l,k}$ be the binary random variable representing the occupancy of the $k$-th cell of the $l$-th ray. The number of cells in the reduced map is denoted by $n_{r,l}\leq n_m$.

Next, let $\mathbf{r}_{l,k+}$ correspond to the event that the $k$-th cell of the $l$-th ray is occupied, cells with lower index (closer cells) are free, and cells with greater index (farther cells) may or may not be occupied, i.e., event $\mathbf{r}_{l,k+}$ occurs when \\$r\in\braces{r\in\{0,1\}^{{n_{r,l}}}\,|\mathbf{r}_{l,1}=0,\mathbf{r}_{l,2}=0,\ldots,\mathbf{r}_{l,k-1}=0,\mathbf{r}_{l,k}=1}$. In other words, the $k$-th cell $\mathbf{r}_{l,k}$ is the closest occupied cell to current pose $X_t$ along the $l$-th ray. For example, see Figure \ref{fig:show_rkplus} that illustrates the event of $\mathbf{r}_{l,k+}$ when $l=1$ and $k=4$ for an one-dimensional cell array. This concept of grouping map outcomes can be easily extended to 2D using ray casting, where a 1D ray is spanning 2D space. The cells considered for the measurement ray are determined with the geometric intersection between the ray and map cell edges.
Then, the forward sensor model is identical for all maps defined by $\mathbf{r}_{l,k+}$, regardless of the occupancy of the cells beyond the $k$-th cell, and the corresponding forward sensor model $p(z_{t,l}|\mathbf{r}_{l,k+},X_{t})$ depends on the distance from $X_t$ to the $k$-th cell. Based on this, we present the mathematical expressions for the exact inverse sensor model, as summarized by \refeqn{RayISMAnswer} in Proposition 1. Later in Section \ref{sec:SA}, these are also rearranged as a computational algorithm.

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{rkplus_1.png}
    \centering
  \includegraphics[width=0.4\textwidth]{rkplus_2.png}  
  \centering
  \includegraphics[width=0.4\textwidth]{rkplus_3.png}
    \centering
  \includegraphics[width=0.4\textwidth]{rkplus_4.png}
  \caption{A robot located to the left of a 1D occupancy grid map $r_l$ composed of $n_{r,l}=6$ grid cells in $4$ cases. In each case, cells $1$--$3$ are free, cell $4$ is occupied, and cells $5$ and $6$ may or may not be occupied. All above outcomes correspond to the event $\mathbf{r}_{l,4+}$.}
  \label{fig:show_rkplus}
\end{figure}

\begin{prop}
For the $l$-th measurement ray, the a posteriori probability of the occupancy of the $k$-th cell, namely the ray inverse sensor model, is given by
\begin{align}
\label{eqn:RayISMAnswer}
P(\mathbf{r}_{l,k}|z_{t,l},X_{1:t},Z_{1:t-1})&=\eta_{t,l}\tilde P(\mathbf{r}_{l,k}|z_{t,l},X_{1:t},Z_{1:t-1}),
\end{align}
where the unnormalized probability of the inverse sensor model is defined as
\begin{align}
\label{eqn:Unnormalized}
& \tilde P(\mathbf{r}_{l,k}|z_{t,l},X_{1:t},Z_{1:t-1})%\nonumber\\&
=P(\mathbf{r}_{l,k}|X_{1:t-1},Z_{1:t-1})\nonumber\\
&\quad\times 
\bigg[\sum_{i=1}^{k-1}\bigg\{\prod_{j=0}^{i-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1})\bigg\}%\nonumber\\
%&\quad\times 
p(z_{t,l}|\mathbf{r}_{l,i+},X_t)P(\mathbf{r}_{l,i}|X_{1:t-1},Z_{1:t-1})\bigg]\nonumber\\
&\quad + \bigg\{\prod_{j=0}^{k-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1})\bigg\}%\nonumber\\
%&\quad\times 
p(z_{t,l}|\mathbf{r}_{l,k+},X_t)P(\mathbf{r}_{l,k}|X_{1:t-1},Z_{1:t-1}),
\end{align}
where $P(\bar{\mathbf{r}}_{l,0}|X_{1:t-1},Z_{1:t-1})=P(\mathbf{r}_{l,n_r+1}|X_{1:t-1},Z_{1:t-1})=1$ is chosen for convenience and $p(z_{t,l}|\mathbf{r}_{l,(n_r+1)+},X_t)$ represents the probability density of the measurement when all of cells in the field of view of the $l$-th ray is not occupied. The normalizer $\eta_{t,l}$ is given by
\begin{align}
\label{eqn:allEta}
\eta_{t,l}
&=
\bigg[\sum_{i=1}^{n_{r,l}+1}\bigg\{\prod_{j=0}^{i-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1})\bigg\}\nonumber\\&\quad\times p(z_{t,l}|\mathbf{r}_{l,i+},X_t)P(\mathbf{r}_{l,i}|X_{1:t-1},Z_{1:t-1})\bigg]^{-1},
\end{align}
and it is independent of the cell index $k$.
\end{prop}
\begin{proof}
See Appendix.
\end{proof}

@@

\subsection{Summary of Algorithm}\label{sec:SA}

In short, the proposed scan inverse sensor model is computed by \refeqn{RayISMAnswer}-\refeqn{RayByRayScanISM}. These are summarized in Algorithm \ref{alg:RayByRayISM} as a computationally efficient, recursive algorithm that avoids several repeated calculations of the same quantity. This algorithm utilizes temporary variables, where the required computational resources are minimized by computing the updated occupancy probabilities of all grid cells along a measurement ray together. Note that this function is only considering $l$-th ray at the $t$-th time step, where probabilities are subject to conditions on $X_{1:t},Z_{1:t-1},z_{t,1:l-1}$, so these are removed from the algorithm for simplicity.

@@

% More simple (subscripts omitted)

\begin{algorithm}[H]
	Function: $P(\mathbf{r}_k|z)=\text{InverseSensorModel}(P(\mathbf{r}_k),z)$ $\forall$ $k\in\braces{1,2,\ldots,n_{r}}$\;
	Initialize $\eta^{-1}=0$ and $P(\bar{\mathbf{r}}_{0})=1$\;
	\For{$k=1,2,\ldots,n_{r}$}{
		$P(\mathbf{r}_{k+}) = P(\bar{\mathbf{r}}_{0:k-1})P(\mathbf{r}_{k})$\;
		$P(\bar{\mathbf{r}}_{0:k})=P(\bar{\mathbf{r}}_{0:k-1})(1-P(\mathbf{r}_{k}))$\;
    		$a_\text{temp}=P(\mathbf{r}_{k+})p(z_l|\mathbf{r}_{k+},X)$\;
   		$\tilde P(\mathbf{r}_{k}|z)=P(\mathbf{r}_{k})\eta^{-1}_{t,l}+a_\text{temp}$\;
   		$\eta^{-1}=\eta^{-1}+a_\text{temp}$\;
	}
	$\eta^{-1}=\eta^{-1}+P(\bar{\mathbf{r}}_{0:k})p(z_\text{max})$\;
	Return $P(\mathbf{r}_{k}|z)=\eta\tilde P(\mathbf{r}_{k}|z)$ for all $k\in\braces{1,2,\ldots,n_{r}}$\;
\caption{Inverse Sensor Model of an Individual Measurement Ray}
\label{alg:RayByRayISM}
\end{algorithm}

@@

We present an algorithm pseudocode providing the necessary steps to obtain the objective function for a single measurement ray (Algorithm \ref{alg:RayExpectedEntropyGain}). Much like the algorithm pseudocode for the inverse sensor model (Algorithm \ref{alg:RayByRayISM}), the variable $a_\text{temp}$ serves as an intermediate variable designed to avoid repeated calculations.
Since this algorithm operates as a function, fixed indices and condition variables are removed for simplification.
